JuliaをRMarkdownで使うテスト

### 2022-02-16 docs/materials/julia_test.Rmd
update julia_test.Rmd

---
title: "JuliaをRMarkdownで使うテスト"
output: html_document
---

@@

```{julia}
ENV["LD_LIBRARY_PATH"] = ""
```

@@

```{julia}
import Pkg
Pkg.update()
Pkg.add("StatsPlots")
Pkg.add("Turing")
Pkg.precompile()
```

>>>>

# JuliaをRMarkdownで使うテスト

@@

```{julia}
ENV["LD_LIBRARY_PATH"] = ""
```
using Distributions
using Random

@@

```{julia}
import Pkg
Pkg.update()
Pkg.add("Distributions")
Pkg.add("Random")
Pkg.add("SymPy")
Pkg.add("StatsPlots")
Pkg.add("Turing")
Pkg.precompile()
```
